\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-04 doc/USER_MANUAL/manual_SPECFEM3D.tex
added comments about other meshers: GiD, Gmsh, and TetGen.

The SPECFEM3D software package relies on the Scotch library to partition the meshes created with CUBIT. Because it is not standard, the path of this library needs to be set with the option \texttt{-{}-with-scotch-lib}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-lib=/opt/scotch/gcc64/lib
\end{lyxcode}

>>>>

The SPECFEM3D software package relies on the Scotch library to partition the meshes created with CUBIT.
Note that we use CUBIT to create meshes of hexahedra, but other packages can be used as well, for instance GiD from http://gid.cimne.upc.es, Gmsh from http://geuz.org/gmsh or even TetGen from http://tetgen.berlios.de (TetGen generates tetrahedra, but each of them can easily be decomposed into four hexahedra as shown in the picture of the TetGen logo at http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif ).

The path to the SCOTCH library needs to be set with the option \texttt{-{}-with-scotch-lib}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-lib=/opt/scotch/gcc64/lib
\end{lyxcode}
